SDR enhancement by clouds

### 2024-03-19 article/article.Rmd
Commit 2024-03-19 17:16
Commit 2024-03-19 18:16

<!-- Define CE and ECE -->
In this study, we define as cloud enhancement events (CE) the cases when the measured
global horizontal irradiance (GHI) at ground level, exceeds the expected value under
clear-sky conditions.
Similar, we define the extreme cloud enhancement events (ECE), the cases when GHI,
exceeds the Total Solar Irradiance on horizontal plane at ground level.
Although the duration of these bursts varies form instantaneous to several minutes,
here we are constrained by the recorded data, to one-minute steps.

@@

<!-- Data selection -->
To preserve an unbiased representation of the data we applied a constrain similar
the one used by @CastillejoCuberos2020. Where, for each valid hour of day, there
must exist at list 45 minutes of valid measurements, including night time near
sunrise and sunset. Days with less than 5 valid hours are rejected completely.
<!--# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7),
otherwise all data for this day is flagged as invalid. There must be at least This
work valid data 45 min of valid data (Tests 1–7) for an hour to be flagged as valid,
otherwise all minute data for this hour is flagged as invalid. -->
Furthermore, due to the significant measurement uncertainty when the Sun is near the
horizon, and to some systematic obstructions by nearby buildings, we have excluded
all measurements with solar zenith angle (SZA) greater than $`r 90-BIO_ELEVA`^\circ$.

@@

The recording of the signal is the one-minute average.
Thus we will refer to this time scale as a cloud enhancement event (CE).

@@

We decided to use the Libradtran [@Emde2016] radiation transfer model, to modeled
the clear sky equivalent of GHI, with monthly climatological data of AOD and water
column from the Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998].  Our site
participates in AERONET, where we operate a Cimel photometer, collocated to
the CM-21 pyranometer, since 2003

@@

Furthermore, to account for the Sun's variability in our one-minute GHI measurements,
we adjusted the model's input spectrum integral to the one of the the TSI provided by
NOAA.  Finally, we adjusted for the effect of the Sun - Earth distance, and
calculated the clear sky irradiance value at the horizontal plane by using the cosine
of the corresponding interpolated SZA.  For each period of the year, we used the
appropriate atmospheric profile (afglms or afglmw).  Thus, the modeled GHI_modeled we
can directly compare each measured one minute value of GHI, with the expected clear
sky radiation.

@@

Which is an expected result as these values represent an typical atmosphere in
Thessaloniki with low load of aerosols and humidity, which are the main factor that
attenuate the GHI, excluding clouds.

@@

Where it was needed, for some of edge cases, we also used images from a sky-cam,
along with the manual inspection.

@@

A secondary criteria was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane (Equation \ref{eq:ECE})

@@

Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one minute measurements.
The annual mean over irradiance is
$`r round(yearlyCE[var == "GLB_diff.mean", slope], 2)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 2)`\,W/m^2$
(Figure\ \ref{fig:P-energy-mean}),
but this value is not very useful due the high
variability of this metric.

>>>>

<!-- Define CE and ECE -->
In this study, we define as cloud enhancement events (CE) the cases when the measured
global horizontal irradiance (GHI) at ground level, exceeds the expected value under
clear-sky conditions.
Similar, we define the extreme cloud enhancement events (ECE), the cases when GHI,
exceeds the Total Solar Irradiance on horizontal plane at ground level.
Although the duration of these bursts varies from instantaneous to several minutes,
here we are constrained by the recorded data, to one-minute steps.

@@

<!-- Data selection -->
To preserve an unbiased representation of the data we applied a constraint similar
the one used by @CastillejoCuberos2020. Where, for each valid hour of day, there
must exist at list 45 minutes of valid measurements, including nighttime near
sunrise and sunset. Days with less than 5 valid hours are rejected completely.
<!--# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7),
otherwise all data for this day is flagged as invalid. There must be at least This
work valid data 45 min of valid data (Tests 1–7) for an hour to be flagged as valid,
otherwise all minute data for this hour is flagged as invalid. -->
Furthermore, due to the significant measurement uncertainty when the Sun is near the
horizon, and to some systematic obstructions by nearby buildings, we have excluded
all measurements with solar zenith angle (SZA) greater than $`r 90-BIO_ELEVA`^\circ$.

@@

The recording of the signal is the one-minute average.
Thus, we will refer to this timescale as a cloud enhancement event (CE).

@@

We decided to use the Libradtran [@Emde2016] radiation transfer model, to model
the clear sky equivalent of GHI, with monthly climatological data of AOD and water
column from the Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998].  Our site
participates in AERONET, where we operate a Cimel photometer, collocated to
the CM-21 pyranometer, since 2003

@@

Furthermore, to account for the Sun's variability in our one-minute GHI measurements,
we adjusted the model's input spectrum integral to the one of the TSI provided by
NOAA.  Finally, we adjusted for the effect of the Sun - Earth distance, and
calculated the clear sky irradiance value at the horizontal plane by using the cosine
of the corresponding interpolated SZA.  For each period of the year, we used the
appropriate atmospheric profile (afglms or afglmw).  Thus, the modeled GHI_modeled we
can directly compare each measured one minute value of GHI, with the expected clear
sky radiation.

@@

Which is an expected result as these values represent a typical atmosphere in
Thessaloniki with low load of aerosols and humidity, which are the main factor that
attenuate the GHI, excluding clouds.

@@

Where it was needed, for some of the edge cases, we also used images from a sky-cam,
along with the manual inspection.

@@

A secondary criterion was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane (Equation \ref{eq:ECE})

@@

Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one-minute measurements.
The annual mean over irradiance is
$`r round(yearlyCE[var == "GLB_diff.mean", slope], 2)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 2)`\,W/m^2$
(Figure\ \ref{fig:P-energy-mean}),
but this value is not very useful due the high
variability of this metric.
